Exploring SSA Optimization Techniques

### 2014-11-12 doc/paper.tex
Added itm_lit and itm_undef docs

\subsection{Considerations}
\subsubsection{Platform incompatibilities}
There is a way compiler-based constant folding might stand in the way of the 
programmer, as described by~Wikipedia~\cite{cfld_cross}. Mostly the compiler can do this when folding
away instructions  operating on floating point operands, because different targets may compute 
floating point operations differently. Therefore cross-compilation becomes an 
issue; if a floating point instruction for target $Y$ normally yielding $V_y$, it 
yields $V_x$ when folded away by target $X$, causing different semantics before and 
after optimisation.

@@

>>>>

\subsection{Considerations}
\subsubsection{Platform incompatibilities}
There is a way compiler-based constant folding might stand in the way of the 
programmer. Mostly the compiler can do this when folding
away instructions  operating on floating point operands, because different targets may compute 
floating point operations differently. Therefore cross-compilation becomes an 
issue; if a floating point instruction for target $Y$ normally yielding $V_y$, it 
yields $V_x$ when folded away by target $X$, causing different semantics before and 
after optimisation.\cite{cfld_cross}

@@

Then there has to be a way to store literals (both floating point and integral)
and \verb+undef+ constants. These structures are trivial:

\begin{lstlisting}
struct itm_literal {
	/* expression base */
	struct itm_expr base;

	/* value, sharing memory */
	union {
		long long i;
		double f;
	} value;
};

struct itm_undef {
	/* expression base */
	struct itm_expr base;
};
\end{lstlisting}
